Commit Rater

### 2015-08-26 presentations/paper/conclusion.tex
Fix spelling, mostly Marco's
Add a todo
Restate summary so that it only mentions repo-level analysis

In this paper, we presented an application used to rate commit messages of Git repositories. Data extraction is done by cloning the repositories. Data synthesis is based on several separate criteria -- some official, some set by us personally. Finally, data analysis is done by comparing the various authors and repositories against each other\TODO{is that true?}.

Only one of our research question has been answered positively: ``good'' commits were recognized by the aformentioned criteria. However, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.

>>>>

\TODO{Etwas abschwächen}

In this paper, we presented an application used to rate commit messages of Git repositories. Data extraction is done by cloning the repositories. Data synthesis is based on several separate criteria -- some official, some set by us personally. Finally, data analysis is done by comparing a set of repositories against each other.

Only one of our research question has been answered positively: ``good'' commits were recognized by the aforementioned criteria. However, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.
